### 2021-07-04 docs/manuscript/manuscript.tex
fix typo: gen -> gene
Cite Scikit-Bio

In our model the morphogen could interact with any of the three genes on the
GRN, but could not be affected by them. The morphogenetic field was defined by
an unidimensional array of 30 isogenic cells exposed to the morphogen
concentration gradient (Fig~\ref{fig:model}C). The initial concentration of
each gen product in all cells was set to 1 in all simulations.\\

@@

Later we calculated the distance between all the pairs of tensors and we
performed a Neighbor Joining clustering using the package Scikit Bio 0.5.5 from
Python 3.

@@

With this matrix we then calculated a distance matrix in which each element
consisted in the Hamming distance between the row vectors in matrix $T$ between
each pair of topologies. We then performed a clustering of these topologies
using the Neighbor Joining method in the Scikit Bio package.

>>>>

In our model the morphogen could interact with any of the three genes on the
GRN, but could not be affected by them. The morphogenetic field was defined by
an unidimensional array of 30 isogenic cells exposed to the morphogen
concentration gradient (Fig~\ref{fig:model}C). The initial concentration of
each gene product in all cells was set to 1 in all simulations.\\

@@

Later we calculated the distance between all the pairs of tensors and we
performed a Neighbor Joining clustering using the package Scikit Bio 0.5.5 from
Python 3~\cite{skbio2020}.

@@

With this matrix we then calculated a distance matrix in which each element
consisted in the Hamming distance between the row vectors in matrix $T$ between
each pair of topologies. We then clustered the topologies based on the
Neighbor Joining method, as implemented in the Scikit Bio
package~\cite{skbio2020}.
